Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae

### 2020-11-10 conclusion.tex
Fixed typo in the conclusions.

The detection of GW from CCSN may help improve our current understanding of the explosion mechanism of massive stars.  
In this paper we have proposed an explorary method to infer PNS properties using an approach based on GW associated with convective oscillations of PNS. As shown by~\cite{Torres:2019b} buoyancy-driven g-modes are excited in numerical simulations of CCSN and their time-frequency evolution is linked to the physical properties of the compact remnant through universal relations. Such modes are responsible for a significant fraction of the highly stochastic GW emitted after core bounce. The findings reported in this paper suggest that PNS asteroseismology might be within reach of current and third-generation GW detectors.

>>>>

The detection of GW from CCSN may help improve our current understanding of the explosion mechanism of massive stars.  
In this paper we have proposed an exploratory method to infer PNS properties using an approach based on GW associated with convective oscillations of PNS. As shown by~\cite{Torres:2019b} buoyancy-driven g-modes are excited in numerical simulations of CCSN and their time-frequency evolution is linked to the physical properties of the compact remnant through universal relations. Such modes are responsible for a significant fraction of the highly stochastic GW emitted after core bounce. The findings reported in this paper suggest that PNS asteroseismology might be within reach of current and third-generation GW detectors.
